logbook simulations

### 2020-03-28 simulation_study/README.Rmd
clean up repository remove unneccesary files

This is the log of simulations.

# Simulations

@@

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
datasets <- c("ace", "ptsd", "nudging", "software", "wilson")
knitr::opts_chunk$set(echo = FALSE)
```

@@

### extract simulation results nb 
```{bash}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output

@@

```{bash}
# on own device
asreview plot asreview-thesis/simulation_output
```

@@

Checkout hyperopt SCTW
Nudging dataset doesn't optimize well? 
```{r}
todo <- huh(todo, "SCTW", "one", "nudging")
```

@@

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556

# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
```

```{r}
todo <- busy(todo, c("LCTW", "RCTW"), "one", "ace")
```

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
```

(re)Simulate BCTW models

@@

@@

```{r}
lubridate::date("2020-03-24")
# todo <- busy(todo, "SCTW", "one", datasets[2:5])
```

Process BCTW models into table
 - python script to extract statistics

Checkout what happened with NCDW and other errors in hpcbatch

@@

Simulate LCTW, RCTW and NCTW models

@@

>>>>

The log of the simulation study.

- hpoptimization. 
  - Sripts for hyperparameter optimization
  - 
- simulation 
  - scripts for simulation studies

@@

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
datasets <- c("ace", "nudging","ptsd",  "software", "wilson")
knitr::opts_chunk$set(echo = FALSE)
```

@@

### extract simulation results nb 
```{bash, eval = FALSE}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output

@@

```{bash, eval = FALSE}
# on own device
asreview plot asreview-thesis/simulation_output
```

@@

Checkout hyperopt SCTW
Nudging dataset doesn't optimize well? 
```{r}
todo <- huh(todo, "SCTW", "one", "nudging")
todo <- check(todo, "SCTW", "one", "nudging")
```

@@

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157

# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
```

```{r}
todo <- busy(todo, c("LCTW", "RCTW"), "one", datasets)
```

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
# error 
# accidentally got killed while downgrading tensorflow at the same time. 
# run again, 7815147

# NCDW for remaining datasets

@@

Optimize BCTW model 6 datasets (for paper)
```{bash, eval = FALSE}
./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
# create config file (BMTW (M=mixed)) 
asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
# move config to device
scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/

# run simulations (on own device)

# see script

@@

```{r}
lubridate::date("2020-03-27")
# todo <- busy(todo, "SCTW", "one", datasets[2:5])

Process BCTW models simulations into table
 - python script to extract statistics

Create checklist table for simulations

Checkout what happened with NCDW and other errors in hpcbatch 
```{bash, eval = FALSE}
# retest with hall dataset 
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d hall -r 23 # 7843185
```

@@

Simulate LCTW, RCTW and NCTW models 
   - create config files
   - run simulation

@@

Move all hyperopt results to harddrive

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active /Volumes/Gerbrich/asreview/archive/output

scp -r gerbrich@cartesius.surfsara.nl:/output/active/nb_max_random_triple_tfidf ~

scp -r gerbrich@cartesius.surfsara.nl:/asreview/output/active/nb_max_random_triple_tfidf/ /Volumes/Gerbrich/asreview/archive/output
